Manuscript Te example

### 2020-01-30 ManuscriptTe.Rmd
bug fixes

#Microclimate calculations
```{r}
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
dat=read.csv("microclimate_C1.csv", sep=",", na.strings = c("-49.99","NA"))
```
```{r}
#ANALYZE SURFACE ROUGHNESS AND PROFILES
C1all$day=  as.POSIXlt(as.character(C1all$datetime),tz='MST', format="%m/%d/%Y %H:%M")$mday
C1all$hour=as.POSIXlt(as.character(C1all$datetime),tz='MST', format="%m/%d/%Y %H:%M")$hour

@@

u.seq3= sapply(z.seq, FUN=wind_speed_profile_segment, u_r=C1.sub[hr, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], zr=c(0.25,0.5,1,1.5), z0=rep(z0[hr],4))

@@

```
```{r}
#plot by date time
dat.dh$Jhr= dat.dh$J +dat.dh$hour/24

>>>>

#Microclimate calculations
```{r}
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
C1all=read.csv("microclimate_C1.csv", sep=",", na.strings = c("-49.99","NA"))
```

```{r}
#ANALYZE SURFACE ROUGHNESS AND PROFILES
C1all$day=as.POSIXlt(as.character(C1all$datetime), tz='MST', format="%m/%d/%Y %H:%M")$mday
C1all$hour=as.POSIXlt(as.character(C1all$datetime), tz='MST', format="%m/%d/%Y %H:%M")$hour

@@

u.seq3= sapply(z.seq, FUN=wind_speed_profile_segment, u_r=C1.sub[hr, c("Wind0.5m","Wind1m","Wind1.5m")], zr=c(0.5,1,1.5), z0=rep(z0[hr],3))

@@

```{r}
#plot by date time
dat.dh$Jhr= dat.dh$J +dat.dh$hour/24
